Splitting it up: the \pkg{spduration} split-population duration regression package

### 2015-10-15 manuscript.Rmd
started working on replication script

We begin by loading the package and formatting the data appropriately. 
\small
\begin{verbatim}
> library(spduration)
> new.coup.data <- add_duration(coup.data, "coup", unitID="countryid", tID="year", 
+   freq="year")
\end{verbatim}

\normalsize
The \texttt{add}\_\texttt{duration} function takes as input a data frame with a binary response variable (in this example, "coup"") that measures the occurrence of the event, or failure, recorded over discrete time periods, and produces a data frame with a duration variable (named "duration") for each spell as well as a binary variable ("atrisk") that is constant across the spell and indicates whether the spell ended in failure. These are then used as response variables for the formula in the `spdur` function. Though the data used in this example are recorded annually, the function supports annual, monthly, or daily data. We begin by fitting first a Weibull and then a log-logistic split-population duration model using the coups data, including the measure of coup risk in the logit (risk) equation. 
\small
\begin{verbatim}
> weib.model <- spdur(duration~Military.Regime+Instability+Recent.War+Regional.Conflict,
+ 	 	atrisk~Coup.Risk+GDP.cap.+Military.Regime+
+ 	 	Recent.War+Regional.Conflict+
+ 	 	South.Am.+Central.Am.,data=new.coup.data)
> loglog.model <- spdur(duration~Military.Regime+Instability+Recent.War+Regional.Conflict,
+  	 	atrisk~Coup.Risk+GDP.cap.+Military.Regime+
+  	 	Recent.War+Regional.Conflict+
+ 	 	South.Am.+Central.Am.,data=new.coup.data,distr="loglog")
\end{verbatim}

\normalsize  
Using the \texttt{summary} function on either model object will produce standard output showing the model formula, estimates for the duration and risk equations, and test statistics with $p$-values. One may also use the \texttt{AIC} and \texttt{BIC} function to calculate the information criterion statistics for \texttt{spdur} objects.  
\small
\begin{verbatim}
> AIC(weib.model)
[1] 1120.774
> AIC(loglog.model)
[1] 1111.908
> BIC(weib.model)
[1] 1209.577
> BIC(loglog.model)
[1] 1200.711
\end{verbatim}

@@

```{r, include = FALSE}
library(foreign)
library(magrittr)
library(ggplot2)
library(xtable)
library(scales)

>>>>

We begin by loading the package and formatting the data appropriately. 
```{r, eval=FALSE}
library(spduration)
data(coup.data)
new.coup.data <- add_duration(coup.data, "coup", unitID="countryid", tID="year",
                              freq="year")
```

\normalsize
The \texttt{add}\_\texttt{duration} function takes as input a data frame with a binary response variable (in this example, "coup"") that measures the occurrence of the event, or failure, recorded over discrete time periods, and produces a data frame with a duration variable (named "duration") for each spell as well as a binary variable ("atrisk") that is constant across the spell and indicates whether the spell ended in failure. These are then used as response variables for the formula in the `spdur` function. Though the data used in this example are recorded annually, the function supports annual, monthly, or daily data. We begin by fitting first a Weibull and then a log-logistic split-population duration model using the coups data, including the measure of coup risk in the logit (risk) equation.

```{r models, eval=FALSE}
weib_model <- spdur(
  duration ~ milreg + instab + rwar + regconf,
  atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + camerica,
  data=bscoup)

loglog_model <- spdur(
  duration~Military.Regime+Instability+Recent.War+Regional.Conflict,
  atrisk~Coup.Risk+GDP.cap.+Military.Regime+Recent.War+Regional.Conflict+
South.Am.+Central.Am.,
  data=bscoup, distr="loglog")
```

Using the \code{summary} function on either model object will produce standard output showing the model formula, estimates for the duration and risk equations, and test statistics with $p$-values. One may also use the \code{AIC} and \code{BIC} function to calculate the information criterion statistics for \code{spdur} objects.  
\small
\begin{verbatim}
> AIC(weib.model)
[1] 1120.774
> AIC(loglog.model)
[1] 1111.908
> BIC(weib.model)
[1] 1209.577
> BIC(loglog.model)
[1] 1200.711
\end{verbatim}

@@

```{r rates, include = FALSE}
library(foreign)
library(magrittr)
library(ggplot2)
library(xtable)
library(scales)

### 2015-10-15 manuscript.tex
started working on replication script

We begin by loading the package and formatting the data appropriately.
\small

\begin{verbatim}
> library(spduration)
> new.coup.data <- add_duration(coup.data, "coup", unitID="countryid", tID="year", 
+   freq="year")
\end{verbatim}

\normalsize
The \texttt{add}\_\texttt{duration} function takes as input a data frame
with a binary response variable (in this example, ``coup''``) that
measures the occurrence of the event, or failure, recorded over discrete
time periods, and produces a data frame with a duration variable
(named''duration``) for each spell as well as a binary variable
(''atrisk``) that is constant across the spell and indicates whether the
spell ended in failure. These are then used as response variables for
the formula in the \texttt{spdur} function. Though the data used in this
example are recorded annually, the function supports annual, monthly, or
daily data. We begin by fitting first a Weibull and then a log-logistic
split-population duration model using the coups data, including the
measure of coup risk in the logit (risk) equation. \small

\begin{verbatim}
> weib.model <- spdur(duration~Military.Regime+Instability+Recent.War+Regional.Conflict,
+       atrisk~Coup.Risk+GDP.cap.+Military.Regime+
+       Recent.War+Regional.Conflict+
+       South.Am.+Central.Am.,data=new.coup.data)
> loglog.model <- spdur(duration~Military.Regime+Instability+Recent.War+Regional.Conflict,
+       atrisk~Coup.Risk+GDP.cap.+Military.Regime+
+       Recent.War+Regional.Conflict+
+       South.Am.+Central.Am.,data=new.coup.data,distr="loglog")
\end{verbatim}

\normalsize  
Using the \texttt{summary} function on either model object will produce
standard output showing the model formula, estimates for the duration
and risk equations, and test statistics with \(p\)-values. One may also
use the \texttt{AIC} and \texttt{BIC} function to calculate the
information criterion statistics for \texttt{spdur} objects.\\\small

>>>>

We begin by loading the package and formatting the data appropriately.

\begin{CodeChunk}
\begin{CodeInput}
library(spduration)
data(coup.data)
new.coup.data <- add_duration(coup.data, "coup", unitID="countryid", tID="year",
                              freq="year")
\end{CodeInput}
\end{CodeChunk}

\normalsize
The \texttt{add}\_\texttt{duration} function takes as input a data frame
with a binary response variable (in this example, ``coup''``) that
measures the occurrence of the event, or failure, recorded over discrete
time periods, and produces a data frame with a duration variable
(named''duration``) for each spell as well as a binary variable
(''atrisk``) that is constant across the spell and indicates whether the
spell ended in failure. These are then used as response variables for
the formula in the \texttt{spdur} function. Though the data used in this
example are recorded annually, the function supports annual, monthly, or
daily data. We begin by fitting first a Weibull and then a log-logistic
split-population duration model using the coups data, including the
measure of coup risk in the logit (risk) equation.

\begin{CodeChunk}
\begin{CodeInput}
weib_model <- spdur(
  duration ~ milreg + instab + rwar + regconf,
  atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + camerica,
  data=bscoup)

loglog_model <- spdur(
  duration~Military.Regime+Instability+Recent.War+Regional.Conflict,
  atrisk~Coup.Risk+GDP.cap.+Military.Regime+Recent.War+Regional.Conflict+
South.Am.+Central.Am.,
  data=bscoup, distr="loglog")
\end{CodeInput}
\end{CodeChunk}

Using the \code{summary} function on either model object will produce
standard output showing the model formula, estimates for the duration
and risk equations, and test statistics with \(p\)-values. One may also
use the \code{AIC} and \code{BIC} function to calculate the information
criterion statistics for \code{spdur} objects.\\\small
